State of the Practice for Lattice Boltzmann Method Software

### 2022-02-03 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Additional notes added to Section 5.

In this section we answers \rqref{RQ_CompareArtifacts} by comparing the
artifacts that we observed in LBM repositories to those observed and recommended
for research software in general.  roadmap?

As part of filling in the measurement template the LBM packages were examined
for the presence of artifacts, which were then categorized by frequency. We have
grouped them into common, less common, and rare artifacts in
Table~\ref{artifactspresent}. Common artifacts were found in 16 to 24 ($>$63\%)
of the software packages. Less common artifacts were found in 8 to 15 (30-63\%)
of the software packages. Rare artifacts were found in 1 to 7 ($<$30\%) of the
software packages.

\begin{table}
\begin{center}
\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
\toprule
\textbf{Common} & \textbf{Less Common} & \textbf{Rare} \\
\midrule
Authors / Developers List & Change Log / Release Notes & API Documentation\\
Issue Tracker & Design Documentation & Developer / Contributor Manual\\
Dependency Notes & Functional Spec. / Notes & FAQ / Forum\\
Installation Guide / Instructions & Performance Information & Verification and
Validation Plan\\
Theory Notes & Test Plan / Script / Cases & Video Guide
(including YouTube)\\
List of Related Publications & User Manual/Guide & Requirements Spec.\\
Makefile / Build File & Version Control & \\
README File & & \\
License & & \\
Tutorial & & \\
\bottomrule
\end{tabular}
\caption{Artifacts Present in LBM Packages, Classified by Frequency}
\label{artifactspresent}
\end{center}
\end{table}

@@

>>>>

As part of filling in the measurement template the LBM packages were examined
for the presence of artifacts, which were then categorized by frequency. We have
grouped them into common, less common, and rare artifacts in
Table~\ref{artifactspresent}. Common artifacts were found in 16 to 24 ($>$63\%)
of the software packages. Less common artifacts were found in 8 to 15 (30-63\%)
of the software packages. Rare artifacts were found in 1 to 7 ($<$30\%) of the
software packages. In this section we answers \rqref{RQ_CompareArtifacts} by
comparing the artifacts that we observed in LBM repositories to those observed
and recommended for research software in general.

\begin{table}
\begin{center}
\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
\toprule
\textbf{Common} & \textbf{Less Common} & \textbf{Rare} \\
\midrule
Authors / Developers List & Change Log / Release Notes & API Documentation\\
Issue Tracker & Design Documentation & Developer / Contributor Manual\\
Dependency Notes & Functional Spec. / Notes & FAQ / Forum\\
Installation Guide / Instructions & Performance Information & Verification and
Validation Plan\\
Theory Notes & Test Plan / Script / Cases & Video Guide
(including YouTube)\\
List of Related Publications & User Manual / Guide & Requirements Spec.\\
Makefile / Build File & Version Control & \\
README File & & \\
License & & \\
Tutorial & & \\
\bottomrule
\end{tabular}
\caption{Artifacts Present in LBM Packages, Classified by Frequency}
\label{artifactspresent}
\end{center}
\end{table}

@@

\wss{From Peter: Roadmap - I did see this mentioned, but no specific artifacts
for it. (``rare'' mentions) Code of conduct, policies for team members - do not
recall ever seeing this Citation - definitely saw this several times (``less
common'') Programming style guide - I did see this as part of developers guide
(``rare'') description of team processes - I do recall seeing ``workflow'' detailed
(``rare''). Not sure if this is similar. peer review - This was mentioned a few
times in the interviews, but I do not recall seeing artifacts for this.
checklists - I did see this a few times (``rare'') linters - I did see this
(``rare'') uninstall - I do not recall seeing this.}
